Accelerating Neural Network Training using Arbitrary Precision Approximating Matrix Multiplication Algorithms

### 2021-03-03 latex/MPP21/paper.tex

>>>>

\begin{enumerate}
	\item confirmed that optimal lambda values are with a factor of 4 of theoretical (for these random inputs)
	\item some errors were lower than expected (555 and 7222), we think this is because of fractions that appear in the coefficients of the largest negative powers of lambda
	\item legend is ordered according to theoretical error
	\item not much fluctuation over dimensions
\end{enumerate}
